Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar

### 2022-10-29 FS-CRB-HR-report4.tex
safety

Progress to date includes:
\begin{itemize}
\item Procurement of harmonic radar equipment and tags
\item Tag fabrication (soldering antennae to diodes) in Matt Siderhurst's lab.
\item Preliminary field testing of equipment on Guam.
\item \textbf{Published our research idea as a preprint in the Research Ideas and Outcomes Journal (\href{https://doi.org/10.3897/rio.8.e86422}{Moore and Siderhurst 2022}). This article will be peer reviewed.}
\end{itemize}

@@

Preliminary tests are promising:
\begin{itemize}
	\item Used digital recordings of the RECCO's audio output to locate tags (See Technical Report: Using a Cell Phone as a Datalogger for Handheld Harmonic Radar \url{https://github.com/aubreymoore/Harmonic-Radar/blob/master/experiments/techreport/techreport.pdf})	
	\item Flown the RECCO harmonic radar device attached to a drone (Fig. \ref{fig:drone})
	\item Based on initial flight tests we determined that the audio data recorder we were using was too heavy for use on the drone. We purchased a much smaller and light audio data recorder. Walk tests with this recorder show that we can locate harmonic radar tags by correlating audio recordings with GPS data (Fig. \ref{fig:211109003}).
	\item \textbf{Recent drone flight.}
\end{itemize}

@@

\textbf{On December 18, Aubrey Moore made a presentation on the technology used in this project at a meeting of the Guam Beekeepers Association (GBA). Members of the GBA and the Guam Department of Agriculture are interested in using harmonic radar to track greater banded hornets (GBH), \textit{Vespa tropica}, to their nests so that they can be destroyed. GBH, a recently arrived invasive species which raids honeybee hives, is a serious threat to Guam's nascent beekeeping industry.
}
\section{MONITORING \& EVALUATION}

@@

\section{PROBLEMS ENCOUNTERED THIS REPORTING PERIOD}
\label{impediments}

>>>>

Progress to date includes:
\begin{itemize}
\item Procurement of harmonic radar equipment and tags
\item Tag fabrication (soldering antennae to diodes) in Matt Siderhurst's lab.
\item Preliminary field testing of equipment on Guam.
\item \textbf{Published our research idea as a preprint in the Research Ideas and Outcomes Journal (\href{https://doi.org/10.3897/rio.8.e86422}{Moore and Siderhurst 2022}). This article will be peer reviewed.}
\item \textbf{Continued to investigate the idea of mounting our harmonic radar transceiver on an aerial drone to facilitate automated surveys over large areas (See Methods Development section below). }
\end{itemize}

@@

Preliminary tests are promising:
\begin{itemize}
	\item Used digital recordings of the RECCO's audio output to locate tags (See Technical Report: \href{https://github.com/aubreymoore/Harmonic-Radar/raw/master/experiments/techreport/techreport.pdf}{Using a Cell Phone as a Datalogger for Handheld Harmonic Radar})	
	\item Flown the RECCO harmonic radar device attached to a drone (Fig. \ref{fig:drone})
	\item Based on initial flight tests we determined that the audio data recorder we were using was too heavy for use on the drone. We purchased a much smaller and light audio data recorder. Walk tests with this recorder show that we can locate harmonic radar tags by correlating audio recordings with GPS data (Fig. \ref{fig:211109003}).
	\item \textbf{On June 9, 2022 we flew a drone with our harmonic radar transceiver suspended beneath it. Audio output from the transceiver was recorded on a small audio data recorder. By correlating audio data with the drone's GPS log, we were able to locate harmonic detector tags on the ground (See \href{https://github.com/aubreymoore/Harmonic-Radar/raw/master/experiments/2022-06-09-drone/techreport.pdf}{technical report}).}
\end{itemize}

@@

On December 18, Aubrey Moore made a presentation on the technology used in this project at a meeting of the Guam Beekeepers Association (GBA). Members of the GBA and the Guam Department of Agriculture are interested in using harmonic radar to track greater banded hornets (GBH), \textit{Vespa tropica}, to their nests so that they can be destroyed. GBH, a recently arrived invasive species which raids honeybee hives, is a serious threat to Guam's nascent beekeeping industry.

\section{MONITORING \& EVALUATION}

@@

\section{PROBLEMS ENCOUNTERED DURING THIS REPORTING PERIOD}
\label{impediments}
